---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##開啟"

```{r}
rm(list=ls())
etf4<-read.table("ETF4_2000_2018_d.txt", header = T , fileEncoding = "UTF-8-BOM")
head(etf4)
```

```{r}
etf4<-read.csv("ETF4_2000_2018_d.csv",  fileEncoding='big5',colClasses = c("證券代碼"="character",'id', 'date', 'price'))
head(etf4)
```

```{r}
library(readr)
etf4_csv<-read_csv("ETF4_2000_2018_d.csv")
etf4_csv<-read_csv("ETF4_2000_2018_d.csv", locale = locale(encoding='big5'))
head(etf4_csv)
str(etf4_csv)
```


rm(list=ls())
etf4<-read.table("ETF4_2000_2018_d.txt")
# you will get error message! This is because Chinese characters that cannot be recognized!
# But this works fine in Mac!!!
# But you can add: fileEncoding = 'UTF-8-BOM' to solve the problem!
etf4<-read.table("ETF4_2000_2018_d.txt", fileEncoding = "UTF-8-BOM")
head(etf4)
# Or you can save the .txt as ansi file fromat using notepad
etf4<-read.table("ETF4_2000_2018_d_ansi.txt", header = T)
# You will get error message in Mac
str(etf4)
# change imoprted data types
etf4<-read.table("ETF4_2000_2018_d_ansi.txt", header = T, stringsAsFactors = T, 
                 colClasses = c("證券代碼"="character"))
str(etf4)
head(etf4)